---
title: "Cascade Summer 2024"
output: html_document
---

#remember to turn *KNIT ON SAVE* ON before exporting to website


*This website to test displaying new incoming data for the upcoming field season* 

incorporate - shiny app to easily display data from the 3 lakes? (instead of scrolling through a static page with all the variables) - data from another one folder


# *Time of last update:*
```{r, echo=FALSE}
print(Sys.time())
```


```{r, echo=FALSE}
data(cars)
plot(cars$speed, cars$dist, xlab= "Dat's age", ylab='Reasons to cry', main='Test Plot')
```

# *DID WE HAVE ANY MISSING DATA?*

(check to see if there are 1440 observations 
  - if yes, then print 'yes there were 1440 observations' in green
  - if no, print which times are missing, and add to list of missing data from previous days)
  
for loop through the 3 lakes/csvs?
```{r, echo=FALSE}
# data <- read.csv("your_file.csv")
# num_observations <- nrow(data)
# 
# if (num_observations == 1440) {
#   print('<span style="color:green;">Hooray! There were no missing observations.</span>')
# } else {
#   # Print the message in red text
#   print('<span style="color:red;">No, there were some missing observations.</span>')
#   
#   all_times <- seq(from = as.POSIXct("00:00:00", format = "%H:%M:%S"), 
#                    to = as.POSIXct("23:59:59", format = "%H:%M:%S"), by = "min")
#   data_times <- as.POSIXct(data$time_column, format = "%H:%M:%S")
#   missing_times <- setdiff(all_times, data_times)
#   print(paste("Missing times:", format(missing_times, "%H:%M:%S")))
# }
```

# WERE THERE ANY OUTLIERS IN THE DATA?
(check to see if there are outliers, either quartile method or X standard deviations from the mean)
  - if no outlier, print 'Hooray, there are no outliers detected!' in green
  - if outlier, print 'There were outliers detected' in red, and print the times/rows of outliers, change value to NAs)

# MANUAL CHLOROPHYLL 

# EWS and other fancy stats/math that PIs want (*idea - if any of the EWS alarms go off, have text at the top of the page that there is a bloom!)

