---
title: "Cascade Summer 2024"
output: html_document
---

#remember to turn *KNIT ON SAVE* ON before exporting to website

*This website is to test displaying new incoming data for the upcoming field season* 

Sonde and t-chain data will be updated everyday to show yesterday's data.
Manual chlorophyll will be updated every few days 

incorporate - shiny app to easily display data from the 3 lakes? (instead of scrolling through a static page with all the variables) - data from another one folder


# *Time of last update:*
```{r, echo=FALSE}
print(Sys.time())
```


```{r, echo=FALSE}
data(cars)
plot(cars$speed, cars$dist, xlab= "Dat's age", ylab='Reasons to cry', main='Test Plot')
```


```{r, echo=FALSE, message=FALSE}
library(lubridate)
library(dplyr) 
```


# *DID WE HAVE ANY MISSING DATA YESTERDAY?*
```{r, echo=FALSE}
#HEADER NAMES BECAUSE the first 4 rows in 2019 are BAD
header_names <- c('Date/Time',	'Temp_YSI',	'SpCond_YSI',	'pH_YSI',	'	DO_YSI',	'DOlocalSat_YSI',	'Chl_YSI	BGA_YSI',	'SDL_Battery_YSI	Time_YSI',	'Date_YSI',	'Cond_YSI',	'pH_mV_YSI',	'DOslSat_YSI',	'Chl_RFU_YSI',	'BGA_RFU_YSI',	'	Sonde_Battery_YSI',	'Temp_HYLB',	'SpCond_HYLB',	'pH_HYLB',	'DO_HYLB',	'DOlocalSat_HYLB',	'Chl_HYLB',	'BGA_HYLB',	'SDL_Battery_HYLB',	'Time_HYLB', 'placeholder1', 'placeholder2', 'lake')
```

```{r, echo=FALSE}
folder_path <- "~/desktop/test_website_data/"
csv_files <- list.files(folder_path, pattern = "\\.csv$", full.names = TRUE)

all_data <- lapply(csv_files, function(file) {
  data <- read.csv(file, skip = 4, header = FALSE)
  lake_name <- ifelse(grepl("Peter", file), "Peter", "Paul")
  data$lake <- lake_name
  return(data)
})
combined_data <- bind_rows(all_data)
names(combined_data) <- header_names
combined_data$`Date/Time` <- mdy_hm(combined_data$`Date/Time`)
combined_data$Date <- date(combined_data$`Date/Time`)
combined_data$Time <- format(combined_data$`Date/Time`, "%H:%M")

peter_data <- combined_data %>%
  filter(lake == "Peter") %>%
  select(-lake)

paul_data <- combined_data %>%
  filter(lake == "Paul") %>%
  select(-lake)
```


```{r, echo=FALSE}
lake_data <- list(Peter = peter_data, Paul = paul_data)

for (lake_name in names(lake_data)) {
  current_data <- lake_data[[lake_name]]
  most_recent_date <- max(current_data$Date)
  current_data_recent <- current_data[current_data$Date == most_recent_date, ]
  num_observations <- nrow(current_data_recent)
#for the 1 minute data it will be 1440
  if (num_observations == 288) {
    print(paste("WAHOOWA! There were no missing observations on", most_recent_date, "in", lake_name, "Lake."))
  } else {
    data_times <- current_data_recent$Time
    # Generate all possible times in a day with 5-minute interval. for the summer this will be 1 min
    all_times <- seq(from = as.POSIXct("00:00", format = "%H:%M"),
                     to = as.POSIXct("23:55", format = "%H:%M"), by = "5 min")
    all_times <- format(all_times, "%H:%M")
    missing_times <- all_times[!all_times %in% data_times]
    print(paste("Father Hesburgh has cursed us! There are", length(missing_times), "missing observations on", most_recent_date, 'in', lake_name, "Lake."))
    missing_times_string <- paste(missing_times, collapse = ", ")
    print(paste("Missing times in", lake_name, "Lake:", missing_times_string))
  }
}
```


# WERE THERE ANY OUTLIERS IN THE DATA?
```{r, echo=FALSE}
outlier_vars <- c('Temp_YSI', 'pH_YSI', 'DOlocalSat_YSI', 'Chl_HYLB')
```

  - if no outlier, print 'Hooray, there are no outliers detected!'
  - if outlier, print 'There were outliers detected', and print the times/rows of outliers, change value to NAs)

# MANUAL CHLOROPHYLL 

# EWS and other fancy stats/math that PIs want (*idea - if any of the EWS alarms go off, have text at the top of the page that there is a bloom!)

